Supplementary Materials: The human visual system preserves the hierarchy of 2-dimensional pattern regularity

### 2021-06-29 analysis/analysis.Rmd
png to pdf for some figures

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.png", width = 5.5, height = 8)
```

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_psychophysical.png",  width = 5.5, height = 8)
```

>>>>

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_eeg_rms.pdf", width = 5.5, height = 8)
```

@@

both_plts <- cowplot::plot_grid(p1, p2, ncol = 2, align="hv")
both_plts
ggsave("plots/subgroup_comp_psychophysical.pdf",  width = 5.5, height = 8)
```
